Shifts in water supply and demand drive land cover change across Chile

### 2024-11-05 article/article_nature/article_nature.qmd
actualizar repo

>>>>

To derive the drought indices of water supply and demand we used the ERA5L dataset and the MODIS product, with a monthly frequency for 1981–2023 and 2000–2023, respectively. Drought indices capture historical anomalies of water supply and demand. To quantify each anomaly, the common practice is to derive it following a statistical parametric method in which it is assumed that the statistical distribution of the data is known [@Heim2002]. The use of an erroneous statistical distribution that does not fit the data is usually the highest source of uncertainty [@Laimighofer2022]. In the case of Chile, due to its high degree of climatic variability, it is difficult to choose a proper distribution without previous research that could be applicable throughout its entire extent. We therefore use a non-parametric method for the calculation of the drought indices, following @Farahmand2015.
